Learning constraints in tabular data

### 2016-05-11 Paper/ECAI/tabular.tex
Added Luc's changes

\newcommand{\eccalc}[2]{\ensuremath{#1 = #2}}
\newcommand{\ecrank}[2]{\eccalc{#1}{\mathit{RANK}(#2)}}
\newcommand{\ecfkey}[2]{\ensuremath{\mathit{FOREIGNKEY}(#1,#2)}}
\newcommand{\ecalldiff}[1]{\ensuremath{\mathit{ALLDIFFERENT}(#1)}}
\newcommand{\eclookupf}[4]{\ensuremath{\mathit{LOOKUP}_{\mathit{#4}}(#1, #2, #3)}}
\newcommand{\eclookup}[4]{\eccalc{#1}{\eclookupf{#2}{#3}{#4}{}}}
\newcommand{\eclookupprod}[5]{\eccalc{#1}{#2 \times \eclookupf{#3}{#4}{#5}{}}}
\newcommand{\eclookupfuzzy}[4]{\eccalc{#1}{\eclookupf{#2}{#3}{#4}{fuzzy}}}
\newcommand{\ecperm}[1]{\ensuremath{\mathit{PERMUTATION}(#1)}}
\newcommand{\ecseries}[1]{\ensuremath{\mathit{SERIES}(#1)}}
\newcommand{\ecprod}[3]{\eccalc{#1}{#2 \times #3}}
\newcommand{\ectotal}[3]{\eccalc{#1}{\mathit{PREV}(#1) + #2 - #3}}
\newcommand{\ecproj}[2]{\eccalc{#1}{\mathit{PROJECT}(#2)}}
\newcommand{\ecaggc}[3]{\eccalc{#2}{\mathit{#1}(#3, col)}}
\newcommand{\ecaggr}[3]{\eccalc{#2}{\mathit{#1}(#3, row)}}
\newcommand{\ecsumc}[2]{\eccalc{#1}{\mathit{SUM}(#2, col)}}
\newcommand{\ecsumr}[2]{\eccalc{#1}{\mathit{SUM}(#2, row)}}
\newcommand{\ecaggif}[5]{\eccalc{#2}{\mathit{#1IF}(#3, #4, #5)}}
\newcommand{\ecsumif}[4]{\eccalc{#1}{\mathit{SUMIF}(#2, #3, #4)}}
\newcommand{\ecsumprod}[3]{\eccalc{#1}{\mathit{SUMPRODUCT}(#2, #3)}}

@@

The approach that we will introduce will borrow techniques from logical and relational learning \cite{luc_book}, where
\cite{claudien,lallouet} have studied the discovery of clausal constraints in an inductive logic programming setting, from constraint learning,  where \cite{Quacq,Conacq,modelseeker} have developed several approaches to learn conjunctive constraints in a constraint programming setting,
and from mining in databases,  where e.g. \cite{Shavlik} has applied inductive techniques to discover constraints (such as functional and multi-valued dependencies) in relational databases.  It also builds on work on program synthesis, in particular, on Flashfill \cite{flashfill}, where the definition of function is learned in spreadsheet data from
very few examples.  Our approach contrasts with all of the mentioned approaches (except Modelseeker) in that it focusses
on learning both column- and row-constraints, it contrasts with Flashfill in learning constraints rather than functions.
A more detailed discussion on related work is contained in Section \ref{sec:related_work}.

@@

\item the \textit{\CSignature} defines the properties that the arguments of the predicate must satisfy. That is, the required types of the arguments, together
with possible further restrictions, e.g., on their length. For example, the signature can restrict the types of the arguments to be groups of integers and require that the length of all arguments be equal. \\
In terms of logical and relational learning \cite{luc_book}, such a \CSignature is known as the {\em bias} of the learner, it specifies when the constraint is well-formed.

@@

Depending on the application, a solution to the tabular constraint learning problem may contain \textit{redundant} constraints, cf. \cite{luc_book}. This is because constraints may be logically equivalent or may be implied by other constraints.

More formally, a constraint $c_1(G_1, ... G_n)$ \textit{implies} another constraint~$c_2(G'_1, ..., G'_m)$ whenever
the  following statement holds: $$\forall G_i, G'_j : c_1(G_1, ... G_n) \rightarrow c_2(G'_1, ... G'_m).$$

We shall only consider {\em range-restricted} implications, that is, we shall require that $\{G'_1, ..., G'_m\} \subseteq \{G_1, ..., G_n\}$.
To simplify notation, and in line with logic programming, we shall often make the quantification implicit and simply write this as rules $ c_1(G_1, ... G_n) \rightarrow c_2(G'_1, ... G'_m)$.  We say that the first constraint is more specific than the second, and the second is more general.

@@

\paragraph{Example}
Consider the following implication:
$$\ecperm{G} \rightarrow \ecalldiff{G}$$
(it can be seen in Table~\ref{table:constraints} that both constraints only hold if $G$ is a vector).
In this case the arguments are identical in both constraints.
Given that the problem is to find the set of {\em all} constraints, and that the more general constraint is entailed
by the more specific one, the $ALLDDIFFERENT(G)$ constraint will be {\em redundant}.
So, for most applications, it will be sufficient to output only the most specific one.

@@

Two constraints are \textit{equivalent} if they imply one another. %More formally, $\forall G'_1, ..., G'_n$ s.t. $\{G''_1, ..., G''_n\} = \{G'_1, ..., G'_n\},\, c_1(G'_1, ... G'_n) \leftrightarrow c_2(G''_1, ..., G''_n)$.
An example within the same \template is for the sum over vectors constraint: $G_1 = +(G_2, G_3) \leftrightarrow G_1 = +(G_3, G_2)$. A related example over multiple constraints is $G_1 = +(G_2, G_3) \leftrightarrow G_1 = \textit{SUM}(H)$ with $\textit{size}(H) = 2$ and $G_2 \subset H, G_3 \subset H$.
\luc{Do we really need this, or can we write it in a real equivalence --- conjunctive formula?}

@@

\tias{Make general intro of subsections}

@@

\subsection{Table and group detection}
\tias{0. preprocess: currencies and precentual to numeric, 1. tables from spreadsheets, 2. groups from tables. Ext: could be done interactively.}
\tias{Mention spreadsheet-specific hacks in the exps, not here}
\samuel{Is an example needed? I find no because it is not our main concern but open for discussion}
We chose to implement a naive approach to extract tables as the detection of tables and headers from data is a complex task on its own (\cite{header}) and a sophisticated implementation goes beyond the scope of this paper.
Our approach first detects rectangular collections of data.
It then attempts to identify the header by looking at the type of the first row.
If this row consists only of textual entries, the row is expected to be the header and is removed, if not, the same procedure is applied on the first column.
We suggest to provide tables in general, for well formated data, however, the user will not have to specify tables manually.
\tias{Samuel, what does this mean?}

@@

\subsection{Algorithm}
\tias{1) all templates, order so only once; 2) generate groups that satisfy signature; 3) generate subgroups that satisfy definition}
Our algorithm is illustrated in Algorithm~\ref{algo:tcl} and contains three key steps.
First, constraint templates are ordered such that they can be treated sequentially and each only once.
Then, for each constraint template~$s \in \temps$ we generate a set~$A$ of \textit{group-assignments} that satisfy the \CSignature of~$s$.
Every group assignment assigns a group~$G \in \groups$ to every argument of the template.
In the third step, for every assignments $(G_1, ..., G_n) \in A$ we find all constraints $s(G_1', ... G_n')$ that hold on the data (satisfy the \CFunction), such that every subgroup $G_i' \subseteq G_i$.

\begin{algorithm}[thb]
  \begin{algorithmic}
    \footnotesize
    \State \textbf{Input:} $\groups$ -- groups, $\constraints$ -- \template's, \dependencies -- dependency graph
    \State \textbf{Output:} $C$ -- learned constraints
    \State $C \gets \emptyset$ \Comment{The set of constraints}
  \For{$t \in \constrainttorder(\constraints,\dependencies)$}
  \State $v_1, ..., v_n =$ variables of $T$ \tias{variables not defined, only nr of groups important?}
    \For{$v_1{:}~G_1, \dots, v_n{:}~G_n \in \generategroups(t, \groups, C, \dependencies)$}
      \State $C \gets C \cup \findassignment(t, v_1{:}~G_1, \dots, v_n{:}~G_n, C, \dependencies)$
    \EndFor
  \EndFor\\
\Return $C$
\end{algorithmic}
\caption{Tabular constraint learning}
\label{algo:tcl}
\end{algorithm}

@@

We now describe each of the three steps in more detail.

@@

The \ecrank{v_y}{v_x} constraint does not have any dependencies, however in a restricted version without ties, groups assigned to $v_y$ would always be a permutation of numbers $1, 2, ..., \textit{length}(v_y)$.
\\\\
Constraint templates have to be treated respecting the order, i.e. learning the most general ones first.
The generality ordering thus imposes a partial ordering according to which constraint templates must be learned.

\subsubsection{Candidate group generation}
\tias{find groups, each $n$ groups and $m$ arguments than m-choose-n candidates. instead of generate-and-test we will search for all valid groups. To do so, CSP with signature in logical constraints and properties of each group as data. Example should use constraint syntax}
$\generategroups(\textit{Constraint,GroupSet,Solutions})$ is the function generating tuples of groups (group-assignments~$A$) that may contains subgroups satisfying the constraint.
The goal of this step is to prune out impossible groups from the beginning by looking at their properties rather than their actual content (\CSignature vs \CFunction).

@@

\samuel{TODO: correct code integer groups}\\
Consider the \ecrank{v_r}{v_x} constraint template, then both arguments must be of the same length.
Therefore, assignments containing groups of different length do not have to be considered.
Constraints of the \CSignature cannot always be enforced directly on a group but have to consider whether subgroups could satisfy them.
For example, the \CSignature requires $v_r$ to be integer.
If a numeric group is assigned to $v_r$ then some subgroups may have type float while other may be of type integer, therefore, this this group cannot be discarded.

For some constraints (e.g. sum, max, count) that share the same \CSignature the same set of assignments~$A$ will be found. \tias{so?}

@@

\subsubsection{Satisfying subgroups}
\tias{not set of assignment but single assignment $a$?}
\tias{requires checking for which of the subgroups of the groups the constraint is satisfied. many subgroups of the groups will not satisfy signature, hence no generate-and-test. Instead, we use again satisfiability to both search for the subgroups and verify satisfiab of the sign and definition.} 
$\findassignment(t,a,C_{solutions})$ finds, for all assignments~$a = (G_1, ..., G_n)$ in $A$, the subgroups $G_i' \subseteq G_i$ such that the corresponding constraint $t(G_1', ..., G_n')$ is satisfied (i.e. the \CSignature and \CFunction of~$t$ are satisfied).
For every \template~$t$ an implementation (declarative or imperative) needs to be provided that, given an assignment, finds valid subgroups.

\paragraph{Example}
Consider a group assignment $G_x, G_y$ associated with the arguments $v_x,v_y$ of \ecrank{v_y}{v_x}, then \findassignment selects single vectors $V_y \in G_y, V_x \in G_x$ such that \ecrank{V_y}{V_x} is true.
For example, in Figure~\ref{fig:main_example} the group $G = \range{T_1}{\rangeall}{\rangeto{3}{8}}$ can serve as both $G_x$ and $G_y$.
Then \findassignment could select $V_x$ to be $\range{T_1}{\rangeall}{7}$ and $V_y$ to be $\range{T_1}{\rangeall}{8}$ since \ecrank{\range{T_1}{\rangeall}{7}}{\range{T_1}{\rangeall}{8}} is satisfied in the data.
\\\\
For some constraint templates (most notably aggregates) there may be multiple (overlapping) subgroups of a given group~$G$ for which the template satisfied.
\tias{like min/max? should mention this example in implied constraints. Not sure we should mention this here, how do we remove overlapping, in post-processing? if so, move to later...}
In this case we choose to omit those subgroups that are fully contained within a larger subgroup since this can lead to over-fitting.
If the returned subsets are too large and accidentally include unrelated vectors the user can split such a group.

\subsection{Implementation note}

\paragraph{Constraint solvers}
\tias{stand-alone (with text-based modeling language) versus embedded.}
For each \template, both \generategroups and \findassignment are can be seen as separate constraint satisfaction problems.
Furthermore, declarative languages such as, for example, ASP \cite{whaisasp} and Minizinc \cite{minizinc} provide primitives that make modeling transparent and generic.

@@

\paragraph{Parallelization}
\tias{Do we do this? If not, cut...}
The two for loops in the algorithm can be easily parallelized. Each generated assignment can be checked independently. Templates may not be independent as expressed by the DAG \dependencies. However, each independent component of the DAG (including one component per template not in the DAG) can be verified independently.

\paragraph{Redundancy}
Mention 'largest overlapping subgroup' here?

\paragraph{Constraints}

@@

Generally \CSignature and / or the \CFunction can be relaxed to capture more constraints in the data, however, this also comes at a performance penalty. \samuel{More on this / example?} \tias{Yes, either explain in detail or cut}

\section{Examples}
\subsection{Group generation CSP}
variables from syntax, domain from input groups, filtered using type

Group generation CSP (Sum Product)\\
variables: $R, O_1, O_2$\\
domains: $D(R) = \{ G | G \in {\cal G} \land \numeric(G)\}$, $D(O_1) = \{ G | G \in {\cal G} \land \numeric(G)\}$, $D(O_2) = \{ G | G \in {\cal G} \land \numeric(G)\}$\\
constraints: $\plength(O_1) = \plength(O_2) \geq 2, \pcols(R) = 1, \prows(R) = 1$ % excluded not partial because we don't focus on it much

Translation:
\begin{description}
  \item[Type] Require group that has supertype (e.g. integer => require numeric group, because subgroup might be integer)
  \item[Length] Require group to have exact length (subgroups have the same length)
  \item[Vectors / columns / rows] Require group to have at least the amount of vectors, columns, rows required
  \item[Dependency] Fix dependent variables, for every assignment construct CSP that attempts to find values for the other variables
  \item[Same length / table / orientation] Require groups to gave the same length table ...
\end{description}

\subsection{Subgroup generation}
Sum Product

Implementation: finds subgroups based on assignments\\
Method $Test(G_R, G_{O_1}, G_{O_2})$\\
$If \lnot G_{O_1} < G_{O_2}: Reject~\#~Canonicity$\\
$If data(G_R) = data(G_{O_1}) \bullet data(G_{O_2}): Accept$
\\\\
Method $FindSubgroups(Assignments)$\\
$Return \{ (G_R', G_{O_1}', G_{O_2}') | \exists (G_R, G_{O_1}, G_{O_2}) \in Assignments \land G_R' \subseteq G_R \land G_{O_1}' \subseteq G_{O_1} \land G_{O_2}' \subseteq G_{O_2} \land Test(G_R', G_{O_1}', G_{O_2}') \}$

Register implementation with the system for constraint X

@@

Redundant constraints can be reduced in different ways.
Duplications should be detected in a post-processing step that uses entailment or heuristics to filter constraints.
Accidental constraints may be detected through heuristics, however, they can be also be removed by adding additional data.

@@

\section{Related Work}\label{sec:related_work}
\sergey{key bullet points for Luc and possibly Samuel and me to make related work section}

>>>>

\newcommand{\eccalc}[2]{\ensuremath{#1 = #2}}
\newcommand{\ecrank}[2]{\eccalc{#1}{\mathit{RANK}(#2)}}
\newcommand{\ecfkey}[2]{\ensuremath{FOREIGNKEY(#1,#2)}}
\newcommand{\ecalldiff}[1]{\ensuremath{\mathit{ALLDIFFERENT}(#1)}}
\newcommand{\eclookupf}[4]{\ensuremath{\mathit{LOOKUP}_{\mathit{#4}}(#1, #2, #3)}}
\newcommand{\eclookup}[4]{\eccalc{#1}{\eclookupf{#2}{#3}{#4}{}}}
\newcommand{\eclookupprod}[5]{\eccalc{#1}{#2 \times \eclookupf{#3}{#4}{#5}{}}}
\newcommand{\eclookupfuzzy}[4]{\eccalc{#1}{\eclookupf{#2}{#3}{#4}{fuzzy}}}
\newcommand{\ecperm}[1]{\ensuremath{\mathit{PERMUTATION}(#1)}}
\newcommand{\ecseries}[1]{\ensuremath{\mathit{SERIES}(#1)}}
\newcommand{\ecprod}[3]{\eccalc{#1}{#2 \times #3}}
\newcommand{\ectotal}[3]{\eccalc{#1}{\mathit{PREV}(#1) + #2 - #3}}
\newcommand{\ecproj}[2]{\eccalc{#1}{\mathit{PROJECT}(#2)}}
\newcommand{\ecaggc}[3]{\eccalc{#2}{\mathit{#1}(#3, col)}}
\newcommand{\ecaggr}[3]{\eccalc{#2}{\mathit{#1}(#3, row)}}
\newcommand{\ecsumc}[2]{\eccalc{#1}{\mathit{SUM}(#2, col)}}
\newcommand{\ecsumr}[2]{\eccalc{#1}{\mathit{SUM}(#2, row)}}
\newcommand{\ecaggif}[5]{\eccalc{#2}{\mathit{#1IF}(#3, #4, #5)}}
\newcommand{\ecsumif}[4]{\eccalc{#1}{\mathit{SUMIF}(#2, #3, #4)}}
\newcommand{\ecsumprod}[3]{\eccalc{#1}{\mathit{SUMPRODUCT}(#2, #3)}}

@@

The approach that we will introduce will borrow techniques from logical and relational learning \cite{LucBook}, where
\cite{Claudien,todo:lallouet} have studied the discovery of clausal constraints in an inductive logic programming setting, from constraint learning,  where \cite{Quacq,Conacq,Modelseeker} have developed several approaches to learn conjunctive constraints in a constraint programming setting,
and from mining in databases,  where e.g. \cite{Savlik} has applied inductive techniques to discover constraints (such as functional and multi-valued dependencies) in relational databases.  It also builds on work on program synthesis, in particular, on Flashfill \cite{}, where the definition of function is learned in spreadsheet data from
very few examples.  Our approach contrasts with all of the mentioned approaches (except Modelseeker) in that it focusses
on learning both column- and row-constraints, it contrasts with Flashfill in learning constraints rather than functions.
A more detailed discussion on related work is contained in Section \luc{TODO}.

@@

\item the \textit{\CSignature} defines the properties that the arguments of the predicate must satisfy. That is, the required types of the arguments, together
with possible further restrictions, e.g., on their length. For example, the signature can restrict the types of the arguments to be groups of integers and require that the length of all arguments be equal. \\
In terms of logical and relational learning \cite{bookLuc}, such a \CSignature is known as the {\em bias} of the learner, it specifies when the constraint is well-formed.

@@

Depending on the application, a solution to the tabular constraint learning problem may contain \textit{redundant} constraints, cf. \cite{bookLuc}. This is because constraints may be logically equivalent or may be implied by other constraints.

More formally, a constraint $c_1(G_1, ... G_n)$ \textit{implies} another constraint~$c_2(G'_1, ..., G'_m)$ whenever
the statement $\forall G_i, G'_j : c_1(G_1, ... G_n) \rightarrow c_2(G'_1, ... G'_m)$ holds. To simplify testing,
we shall only consider {\em range-restricted} implications, that is, we shall require that $\{G'_1, ..., G'_m\} \subseteq \{G_1, ..., G_n\}$.
To simplify notation, and in line with logic programming, we shall often make the quantification implicit and simply write this as rules $ c_1(G_1, ... G_n) \rightarrow c_2(G'_1, ... G'_m)$.  We say that the first constraint is more specific than the second, and the second is more general.

@@

\paragraph{Example}
Consider the following implication:
$$PERMUTATION(G) \rightarrow ALLDIFFERENT(G)$$
(it can be seen in Table~\ref{table:constraints} that both constraints only hold if $G$ is a vector).
In this case the arguments are identical in both constraints.
Given that the problem is to find the set of {\em all} constraints, and that the more general constraint is entailed
by the more specific one, the $ALLDDIFFERENT(G)$ constraint will be {\em redundant}.
So, for most applications, it will be sufficient to output only the most specific one.

@@

Two constraints are \textit{equivalent} if they imply one another. %More formally, $\forall G'_1, ..., G'_n$ s.t. $\{G''_1, ..., G''_n\} = \{G'_1, ..., G'_n\},\, c_1(G'_1, ... G'_n) \leftrightarrow c_2(G''_1, ..., G''_n)$.
An example within the same \template is for the sum over vectors constraint: $G_1 = +(G_2, G_3) \leftrightarrow G_1 = +(G_3, G_2)$. A related example over multiple constraints is $G_1 = +(G_2, G_3) \leftrightarrow G_1 = SUM(H)$ with $size(H) = 2$ and $G_2 \subset H, G_3 \subset H$.
\luc{Do we really need this, or can we write it in a real equivalence --- conjunctive formula?}

@@

@@

\subsection{Table and group detection}
\samuel{Is an example needed? I find no because it is not our main concern but open for discussion}
We chose to implement a naive approach to extract tables as the detection of tables and headers from data is a complex task on its own (\cite{header}) and a sophisticated implementation goes beyond the scope of this paper.
Our approach first detects rectangular collections of data.
It then attempts to identify the header by looking at the type of the first row.
If this row consists only of textual entries, the row is expected to be the header and is removed, if not, the same procedure is applied on the first column.
We suggest to provide tables in general, for well formated data, however, the user will not have to specify tables manually.

@@

\subsection{Algorithm}
Our algorithm is illustrated in Algorithm~\ref{algo:tcl} and contains three key steps.
First, constraint templates are ordered such that they can be treated sequentially and each only once.
Then, for each constraint template~$s \in \temps$ we generate a set~$A$ of \textit{group-assignments} that satisfy the \CSignature of~$s$.
Every group assignment assigns a group~$G \in \groups$ to every argument of the template.
In the third step, for every assignments $(G_1, ..., G_n) \in A$ we find all constraints $s(G_1', ... G_n')$ that hold on the data (satisfy the \CFunction), such that every subgroup $G_i' \subseteq G_i$.

\begin{algorithm}[thb]
  \begin{algorithmic}
    \footnotesize
    \State \textbf{Input:} $\groups$ -- groups, $\constraints$ -- \template's, \dependencies -- dependency graph
    \State \textbf{Output:} $C$ -- learned constraints
    \State $C \gets \emptyset$ \Comment{The set of constraints}
  \For{$t \in \constrainttorder(\constraints,\dependencies)$}
  \State $v_1, ..., v_n =$ variables of $T$
    \For{$v_1{:}~G_1, \dots, v_n{:}~G_n \in \generategroups(t, \groups, C, \dependencies)$}
      \State $C \gets C \cup \findassignment(t, v_1{:}~G_1, \dots, v_n{:}~G_n, C, \dependencies)$
    \EndFor
  \EndFor\\
\Return $C$
\end{algorithmic}
\caption{Tabular constraint learning}
\label{algo:tcl}
\end{algorithm}

@@

@@

The \ecrank{v_y}{v_x} constraint does not have any dependencies, however in a restricted version without ties, groups assigned to $v_y$ would always be a permutation of numbers $1, 2, ..., \textit{length}(v_y)$.
\\\\
Most parts of the algorithm could be easily parallelized.
Every connected component in \dependencies can be learned independently.
Within every component, constraint templates have to be treated respecting the order, i.e. learning the most general ones first.
The generality ordering thus imposes a partial ordering according to which constraint templates must be learned.

\subsubsection{Candidate group generation}
$\generategroups(\textit{Constraint,GroupSet,Solutions})$ is the function generating tuples of groups (group-assignments~$A$) that may contains subgroups satisfying the constraint.
The goal of this step is to prune out impossible groups from the beginning by looking at their properties rather than their actual content (\CSignature vs \CFunction).

@@

\samuel{TODO: correct code integer groups}\\
Consider the \ecrank{v_r}{v_x} constraint template, then both arguments must be of the same length.
Therefore, assignments containing groups of different length do not have to be considered.
Constraints of the \CSignature cannot always be enforced directly on a group but have to consider whether subgroups could satisfy them.
For example, the \CSignature requires $v_r$ to be integer.
If a numeric group is assigned to $v_r$ then some subgroups may have type float while other may be of type integer, therefore, this this group cannot be discarted.

For some constraints (e.g. sum, max, count) that share the same \CSignature the same set of assignments~$A$ will be found.

@@

\subsubsection{Subgroup satisfaction search}
$\findassignment(t,A,C_{solutions})$ finds, for all assignments~$a = (G_1, ..., G_n)$ in $A$, the subgroups $G_i' \subseteq G_i$ such that the corresponding constraint $t(G_1', ..., G_n')$ is satisfied (i.e. the \CSignature and \CFunction of~$t$ are satisfied).
For every \template~$t$ an implementation (declarative or imperative) needs to be provided that, given an assignment, finds valid subgroups.

\paragraph{Example}
Consider a group assignment $G_x, G_y$ associated with the arguments $v_x,v_y$ of \ecrank{v_y}{v_x}, then \findassignment selects single vectors $V_y \in G_y, V_x \in G_x$ such that \ecrank{V_y}{V_x} is true.
For example, in Figure~\ref{fig:main_example} the group $G = \range{T_1}{\rangeall}{\rangeto{3}{8}}$ can serve as both $G_x$ and $G_y$.
Then \findassignment could select $V_x$ to be $\range{T_1}{\rangeall}{7}$ and $V_y$ to be $\range{T_1}{\rangeall}{8}$ since \ecrank{\range{T_1}{\rangeall}{7}}{\range{T_1}{\rangeall}{8}} is satisfied in the data.
\\\\
For some constraint templates (most notably aggregates) there may be multiple (overlapping) subgroups of a given group~$G$ for which the template satisfied.
In this case we choose to omit those subgroups that are fully contained within a larger subgroup since this can lead to over-fitting.
If the returned subsets are too large and accidentally include unrelated vectors the user can split such a group.

\subsection{Implementation note}
For each \template, both \generategroups and \findassignment are can be seen as separate constraint satisfaction problems.
Hence, it is natural to solve them using declarative solvers.
Even though each of these problems differ from each other, they are variations that can be modeled using similar techniques.
This also makes it easy to extend the implementation as templates can be easily added (or removed).
Furthermore, declarative languages such as, for example, ASP \cite{whaisasp} and Minizinc \cite{minizinc} provide primitives that make modeling transparent and generic.

@@

\subsection{Constraints}

@@

Generally \CSignature and / or the \CFunction can be relaxed to capture more constraints in the data, however, this also comes at a performance penalty. \samuel{More on this / example?}

@@

Redundant constraints can be reduced in different ways.
Duplications should be detected in a post-processing step that uses entailment or heursitics to filter constraints.
Accidental constraints may be detected through heuristics, however, they can be also be removed by adding additional data.

@@

\section{Related Work}
\sergey{key bullet points for Luc and possibly Samuel and me to make related work section}
